White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2017-09-24 papers/wdmerger_II/paper.tex
Add sponge comment to paper

We terminate the simulation at $t = 10$ seconds, as we have found that for this
particular setup, all of the significant burning has completed by this time. At
this point, the total energy on the domain has become positive, typically about
$10^{51}$ ergs, and has stopped increasing. This means that the system has become
unbound due to nuclear energy release, and that no further meaningful nuclear energy
generation is occurring.

As in Paper I, the region outside the WDs is filled with a low-density ambient
material with $\rho = 10^{-4}\ \text{g / cm}^{-3}$ whose composition and temperature is the
same as that of the WDs. Reactions in this region are unimportant, so for
computational efficiency, we disable all nuclear burning for zones that have
$\rho < 10^6\ \text{g / cm}^{-3}$ and $T < 10^8\ \text{K}$. We have confirmed that
the results do not depend on this choice. The density floor for the simulation is set
at $10^{-5}\ \text{g / cm}^{-3}$ and the temperature floor is $10^7$ K.

>>>>

We terminate the simulation at $t = 9$ seconds, as we have found that for this
particular setup, all of the significant burning has completed by this time. At
this point, the total energy on the domain has become positive, typically about
$10^{51}$ ergs, and has stopped increasing. This means that the system has become
unbound due to nuclear energy release, and that no further meaningful nuclear energy
generation is occurring.

As in Paper I, the region outside the WDs is filled with a low-density ambient
material with $\rho = 10^{-4}\ \text{g / cm}^{-3}$ whose composition and temperature is the
same as that of the WDs. Reactions in this region are unimportant, so for
computational efficiency, we disable all nuclear burning for zones that have
$\rho < 10^6\ \text{g / cm}^{-3}$ and $T < 10^8\ \text{K}$. We have confirmed that
the results do not depend on this choice. A sponge is applied to all gas at a distance
greater than $2.5 \times 10^9$ cm from the origin, which is just larger than the
initial location of the outer edges of the white dwarfs. The sponge damps out the
velocity in this region (see Paper I) to prevent spurious numerical error from dragging
down the global timestep. The density floor for the simulation is set
at $10^{-5}\ \text{g / cm}^{-3}$ and the temperature floor is $10^7$ K.
